Experiments with Synthetic Data

### 2022-07-25 dev/notebooks/real_world.qmd
added plotting function for experiment results

```{julia}
catalogue = AlgorithmicRecourseDynamics.Data.load_real_world()
choices = [:german_credit_numerical, :give_me_some_credit_balanced]
data_sets = filter(p -> p[1] in choices, catalogue)
```

@@

```{julia}
run_experiments(data_sets,models,generators)
```

>>>>

```{julia}
catalogue = AlgorithmicRecourseDynamics.Data.load_real_world()
choices = [:give_me_some_credit_balanced]
data_sets = filter(p -> p[1] in choices, catalogue)
```

@@

```{julia}
results = run_experiments(data_sets,models,generators;save_path=output_path,evaluate_every=10,n_rounds=50)
```

```{julia}
[plot(res) for res in results]
```

### 2022-07-25 dev/notebooks/synthetic.qmd
added plotting function for experiment results

In this notebook we will use toy data to see how endogenous domain shifts and the resulting model shifts can have implications on the validity and cost of algorithmic recourse.

@@

## Experiments

### Data

```{julia}
catalogue = AlgorithmicRecourseDynamics.Data.load_synthetic()
```

```{julia}
using AlgorithmicRecourseDynamics.Models
using Flux
using AlgorithmicRecourseDynamics.Experiments
using AlgorithmicRecourseDynamics.Experiments: Experiment
using CSV, BSON

function _run_one()
    @info "Starting $(key)"

    # Models:
    model = Models.build_mlp()
    λ = 0.1
    model_laplace = Laplace(model, λ=λ)
    M = FluxModel(model)
    M_laplace = LaplaceReduxModel(model_laplace)
    models = (Bayesian=M_laplace, Plugin=M)

    # Pretrain:
    data_train, data_test = Models.train_test_split(counterfactual_data)
    models = map(model -> Models.train(model, data_train; n_epochs=100), models)

    # Generators:
    generators = (
        Greedy=GreedyGenerator(), 
        Generic=GenericGenerator(),
        REVISE=REVISEGenerator(),
        DICE=DiCEGenerator()
    )

    # Variables:
    μ = 0.1
    γ = 0.75
    n_rounds = 10
    n_folds = 5
    T = 1000
    target = 1.0
    experiment = Experiment(data_train, data_test, target, models, generators, 5)

    # Run:
    output = run_experiment(experiment; evaluate_every=2, n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)

    CSV.write(joinpath(output_path,"output_$(key).csv"), output)
    BSON.@save joinpath(output_path,"output_$(key).bson") output
    BSON.@save joinpath(output_path,"experiment_$(key).bson") experiment

    @info "Successfully saved $(key)"

    return output, experiment
end

import AlgorithmicRecourseDynamics: run_experiment
function run_experiment(catalogue::Dict)
    output = [_run_one() for (key,counterfactual_data) in catalogue]
    return output
end
```

```{julia}
choices = [:linearly_separable, :overlapping, :plus_shaped, :balanced_positive_clusters]
data_sets = filter(p -> p[1] in choices, catalogue)
run_experiment(data_sets)
```

```{julia}
BSON.@load joinpath(output_path,"output_linearly_separable.bson") output
```

```{julia}
output[output.name.==:mmd_grid,:]
```

>>>>

@@

```{julia}
catalogue = AlgorithmicRecourseDynamics.Data.load_synthetic()
choices = [:linearly_separable, :overlapping, :plus_shaped, :balanced_positive_clusters]
data_sets = filter(p -> p[1] in choices, catalogue)
```

```{julia}
models = [:FluxModel, :LaplaceReduxModel]
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    :DICE=>DiCEGenerator()
)
```

```{julia}
results = run_experiments(data_sets,models,generators;save_path=output_path,evaluate_every=10,n_rounds=50)
```

```{julia}
[plot(res) for res in results]
```
